A Reduced Representation for Computational Fabrication

### 2013-05-03 thesis/Results.tex
figure caption

\begin{figure*}[t]
\centering
\includegraphics*[clip, width = \linewidth]{figure/ReducerNetworksSuplemental}
\caption{The figure shows all \emph{reducer trees} used in this paper.
\textbf{Smooth caustics:} The smooth caustics tree consists of a spline surface that divides the geometry into an inner surface filled with a transparent material and an outer, void surface. This allows us to approximate displacement mapping.  Here, a single \emph{tuner} is used deform the spline surface.
\textbf{Smooth caustics/texture:} The smooth caustics/texture \emph{reducer tree} splits the object into upper and lower sections using a plane. The upper section then uses the Smooth caustics \emph{reducer tree} to define surface displacements while the lower section uses a set of columns as texture pixels. Here, a single \emph{tuner} solves for the caustic image and a set of \emph{tuners} with regular connectivity solves for the textured image.  \textbf{Deformation/texture:} The object is divided into an outer layer and inner volume using a stratum node. The interior volume is then voxelized and each voxel is assigned a layered material. As in the previous example, the outer layer is divided into columns which are used as pixels for the texture image. The \emph{tuner} setup is also similar to the previous example except the single \emph{tuner} is used to optimize the mechanical behavior of the object. \textbf{Facet caustics:} Here, we build facets by dividing an object into columns and then bisecting the columns horizontally with a plane. The orientation of this plane defines the angle of the facet surface. We use a separate \emph{tuner} to optimize each plane orientation.
\textbf{Subsurface scattering/texture:} The subsurface scattering/texture \emph{reducer tree} partitions the object into an inner volume and outer layer using a \emph{stratum node}. The inner volume is unimportant in this example so we place a constant material there. The outer material is divided into pixels using the \emph{column node}. These columns are filled with layered materials. We optimize each column separately using an associated \emph{tuner}. }
\label{fig:ReducerTreesAdditional}
\end{figure*}

\chapter{Discussion}
\biglet{T}{hrough} the above series of experiments, I will confirm whether \emph{reducer tree} and \emph{tuner network} can allow us to reuse a large number of software components.
In the extreme case, the subsurface scattering algorithm can be obtained by trivially adapting the same \emph{reducer tree} for texture mapping objects.
The power of component reuse is further elucidated by the presence of \emph{column nodes} in most examples and by the reuse of optimization schemes (such as branch and bound) in multiple algorithms.
The \emph{reducer tree} and \emph{tuner network} will make these similarities easy to observe and exploit.
The only component whose reusability was not demonstrated in this proposal is simulation.
In this work, I will aim to fabricate objects with a wide range of physical properties and this necessitates the use of a wide range of simulation algorithms. Finally, once a whole process is configured, it is independent of input geometry and goal parameters. For example, I can run the spatially-varying albedo process with different geometries and input textures

>>>>

\begin{figure*}[t]
\centering
\includegraphics*[clip, width = \linewidth]{figure/ReducerNetworksSuplemental}
\caption{The figure shows all \emph{reducer trees} proposed in this proposal.
\textbf{Smooth caustics:} The smooth caustics tree consists of a spline surface that divides the geometry into an inner surface filled with a transparent material and an outer, void surface. Void material can be used to implement displacement mapping.
Here, a single \emph{tuner} can be used ti deform the spline surface.
\textbf{Smooth caustics/texture:} The smooth caustics/texture \emph{reducer tree} splits the object into upper and lower sections using a plane.
The upper section then uses the Smooth caustics \emph{reducer tree} to define surface displacements while the lower section uses a set of columns as texture pixels.
Here, a single \emph{tuner} solves for the caustic image and a set of \emph{tuners} with regular connectivity solves for the textured image.
\textbf{Deformation/texture:} The object is divided into an outer layer and inner volume using a stratum node.
The interior volume is then voxelized and each voxel is assigned a layered material.
As in the previous example, the outer layer is divided into columns which are used as pixels for the texture image.
The \emph{tuner} setup is also similar to the previous example except the single \emph{tuner} is used to optimize the mechanical behavior of the object.
\textbf{Facet caustics:} Here, I will build facets by dividing an object into columns and then bisecting the columns horizontally with a plane.
The orientation of this plane defines the angle of the facet surface. 
I will use a \emph{tuner network} to optimize for smooth plane orientations.
\textbf{Subsurface scattering/texture:} The subsurface scattering/texture \emph{reducer tree} partitions the object into an inner volume and outer layer using a \emph{stratum node}.
The inner volume is unimportant in this example so I  can place a constant material there.
The outer material is divided into pixels using the \emph{column node}.
These columns are filled with layered materials.
I can optimize each column separately using an associated \emph{tuner}.}
\label{fig:ReducerTreesAdditional}
\end{figure*}
\chapter{Discussion}
\biglet{T}{hrough} the above series of experiments, I will confirm whether \emph{reducer tree} and \emph{tuner network} can allow us to reuse a large number of software components.
In the extreme case, the subsurface scattering algorithm can be obtained by trivially adapting the same \emph{reducer tree} for texture mapping objects.
The power of component reuse is further elucidated by the presence of \emph{column nodes} in most examples and by the reuse of optimization schemes (such as branch and bound) in multiple algorithms.
The \emph{reducer tree} and \emph{tuner network} will make these similarities easy to observe and exploit.
The only component whose reusability was not demonstrated in this proposal is simulation.
In this work, I will aim to fabricate objects with a wide range of physical properties and this necessitates the use of a wide range of simulation algorithms. Finally, once a whole process is configured, it is independent of input geometry and goal parameters. For example, I can run the spatially-varying albedo process with different geometries and input textures
